|

### 2023-01-31 paper.Rmd
Tue Jan 31 10:00:05 CET 2023: update-remote.sh

Unfortunately, as shown in figure \@ref(fig:airfoil-runtime-total), for the experiment conducted on the airfoil dataset with 2 hidden layers a strong negative impact of pre-training can be observed for the median runtime of DAE-GP. If the time spend on pre-training is included into the total runtime, the median duration for pre-trained DAE-GP over all 10 runs is $14706.465$ seconds as opposed to regular DAE-GP that has a median runtime of $5076.448. Even if the time spend

>>>>

```{r python_runtime, echo=FALSE}
REG_TIME=5076.448
PT_TIME=14706.465
PT_TIME_NOSAMPLE=12536.889

Unfortunately, as shown in figure \@ref(fig:airfoil-runtime-total), for the experiment conducted on the airfoil dataset with 2 hidden layers a strong negative impact of pre-training can be observed for the median runtime of DAE-GP. If the time spend on pre-training is included into the total runtime, the median duration for pre-trained DAE-GP over all 10 runs almost tripples from a median runtime of $5076.448$ for regular DAE-GP to $14706.465$ seconds for the pre-trained algorithm. Even in the case where the time spend for pre-training is excluded from the total runtime, pre-training still increases the runtime of DAE-GP to $12536.889$ seconds which
